---
title: "`r knitr::current_input()`"
date: "`r paste('last updated', 
    format(lubridate::now(), ' %d %B %Y'))`"
output:
  html_document: 
    code_folding: show
    highlight: tango
    number_sections: yes
    theme: sandstone
    toc: yes
    toc_depth: 2
    toc_float: true
  pdf_document:
    toc: yes
    number_sections: TRUE
geometry: margin=1in
editor_options: 
  chunk_output_type: console
TAGS:  knit_code,dt,all_labels
---

### Collect knitr::knit_code() examples

echo[TRUE] print code  
eval[TRUE] eval cod  
include[TRUE] print output  

### 0-setup, no output
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,  
                      comment="      ##", 
                      collapse=TRUE)
library(knitr)
library(jimTools)
```


```{r TAGS, eval=FALSE, echo=FALSE}
TAGS <- c("collapse", "chunks", "examples")
```

### 1-evaluate, but include no output
```{r test, eval=TRUE, include=FALSE}
print("hi")
x=4
show_text=FALSE
c_ECHO = FALSE
c_EVAL = FALSE
c_INCLUDE = FALSE


```

### print line numbers
```{r, attr.source='.numberLines'}
if (TRUE) {
  x <- 1:10
  x + 1
}
knitr::knit_exit()
```

### 2-test chunk, include=FALSE 
```{r label=first, include=FALSE}
print("label = first")
```
```{r begin, attr.source='.numberLines'}
print("line1")
print("line2")

```

### 3-use knit_code$get() on test chunk!
```{r label=second, include=TRUE, code=knitr::knit_code$get("first")}
```

### 4-all_labels()
  * includes all labels in document, even if past knit_exit()
```{r all_labels}
print(knitr::all_labels())
```

### 4A-all_labels()
  * includes all labels in document, even if past knit_exit()
```{r all_labels2}
library(data.table)
dt  <- data.table(knitr::all_labels())
dt
```
```{r exit}
knitr::knit_exit()
```
```{r render, eval=FALSE}

file  <- here("rmd", "0064_knit_code.Rmd")
file
rmarkdown::render(
	file, 
	rmarkdown::html_document(), 
#	rmarkdown::pdf_document() ,
  output_file="~/Downloads/print_and_delete/out") 
```
### LEGACY

## 2-output, but do not evaluate
```{r check, eval=FALSE}
print(x)
```

## 3-nothing!
```{r check1, eval=FALSE, include=FALSE}
print(x+2)
```

3A-results='hide', code only
```{r results='hide'}
print(x+2)
print("3A-results=hide")
```

3B-NOT results='hide'
```{r, collapse, collapse=TRUE}
print(x+2)
print("3B-results=NOT hide")
```

4A-conditional
```{r conditional_block, echo=show_text, eval=show_text, include=show_text }

# see in 1-setup
print("show_text is TRUE")
```

4B-conditional
```{r conditional_blockB, echo=!show_text, eval=!show_text, include=!show_text }

# see in 1-setup
print("show_text is TRUE")
```

## 7A-collapse=TRUE
```{r collapse=TRUE }
print("one")
print("two")
```

## 7B-collapse=FALSE
```{r, label="7B", collapse=FALSE, eval=c_eval, include=c_include, echo =
  c_echo}
print("one")
print("two")
```


## 20-list extra-all chunk options
```{r chunk_options, include=show_text, collapse=TRUE}
str(knitr::opts_chunk$get())
```



## 21-knitr::read_chunk from external .R file WORKS!
[REF:] (https://bookdown.org/yihui/rmarkdown-cookbook/read-chunk.html)
```{r read, cache=FALSE }

#  knitr::read_chunk('~/code/r_try_things_here/rmd/file_for_read_chunk.R')
x  <- knitr::read_chunk("file_for_read_chunk.R")


```

## 22-knit_code(), include code from label="7B"
```{r, echo = !c_ECHO, eval = !c_EVAL, include=!c_INCLUDE, code=knitr::knit_code$get("7B")}

```
### create tempfiles and tempdir (original:  see jimTools)
```{r fake}

## returns names of proposed fake files
create_fake_files  <- function() {
  pattern=paste0(1:5,"_")
  pattern

  tempdir = tempdir()
  tempdir

  fileext = ".mp3"

  tempfile(pattern , tempdir, fileext) 
}

fake_files  <- create_fake_files()
fake_files

fake_files[1]
writeLines(con = fake_files[1], 
           c( "```{r chunk}", 
             "\n",
          "knitr::current_input()",
           "```")
           )

remove_fake_files   <- function() {
  unlink(fake_files)

```

```{r knit_fake_fils}
# can't find file
knitr::knit(fakes_files[1])

```

```{r question, eval=F, include=F}

In a file named `my_file.Rmd` I use kntr::current_input() in both:

yaml:
---
title: "`r knitr::current_input()`"
---

and in a code chunk:
```{r file}
file  <- knitr::current_input()
```

Works great when I run this one line to render:

rmarkdown::render(input="my_file.Rmd")



But I am lazy and prefer knitr figure the file name to render, ie PRIOR to knitting the  document, even if this requires two passes.

My confusion may be conceptual and appreciate any documentation suggestions.

(I nvim and not Rstudio.)



```




---

(I stole this code)
figure this out!
* find all chunks
* neatly numbers them?

```{r challenge_regex, eval=FALSE , echo=FALSE  }

name_chunks_mlr3book = function() {

  here()
  # full.names = FALSE for file names only
  rmds = list.files(here("rmd"), 
    pattern = "\\.Rmd$", full.names = TRUE, recursive = TRUE)

  rmds

  pattern = "^([[:space:]]*```\\{[rR])([[:alnum:] -]*)(.*\\})[[:space:]]*$"
  
  for (rmd in rmds) {
    message(sprintf("Renaming chunks in '%s'", basename(rmd)))

    # read all the lines
    lines = readLines(rmd)

    # which lines, spaces, then ```, anything, then }
    # misses a few with ::spaces:: after final }
    ii  <- which(
                 stringr::str_detect(
                                     lines, 
                                     "^[[:space:]]*```\\{[rR].*\\}$"))


    # START HERE
    labels = sprintf("%s-%03i", stringi::stri_replace_last_fixed(basename(rmd), ".Rmd", ""), seq_along(ii))

    lines[ii] = stringi::stri_replace_first_regex(lines[ii], pattern, sprintf("$1 %s$3", labels))

    writeLines(stringi::stri_trim_right(lines), con = rmd)
  }

  invisible(TRUE)
}
```
STop
```{r}
knitr::knit_exit()
```

render from code, to html
```{r eval=FALSE}

file  <- "0064_knit_code.Rmd"
file  <- here("rmd", file)
file

rmarkdown::render(
	file, 
	#rmarkdown::html_document(), 
	rmarkdown::pdf_document() ,
  output_file="~/Downloads/print_and_delete/out") 
  
```

