
---
title: "`r knitr::current_input()`"
date: "`r paste('last updated', 
    format(lubridate::now(), ' %d %B %Y'))`"
output:   
  html_document:  
        code_folding: show
        toc: true 
        toc_depth: 4
        toc_float: true
        mathjax: default
  pdf_document:   
    latex_engine: xelatex  
    toc: true
    toc_depth:  4 
    extra_dependencies: ["amssymb", "bbm", "threeparttable"]
fontsize: 11pt   
geometry: margin=0.5in,top=0.25in   
TAGS:  math, latex
---

## This file:  mostly cheat sheet.
## More equations in 0004B

#### Embed `modified` latex equations inside Rmd; compile with knitr
Seems to work Great (as long as no latex packages needed)

  *  REF: https://gist.github.com/derekmcloughlin/896da22518ef2f3d81b0
  *  Best, so far:   https://www.overleaf.com/learn


### Special
<!--
Does not work:
$\newcommand{\Z}{\mathbb{Z}}$
$\Z$

$\N \quad \Z \quad \Q \quad \R \quad \C$
-->

In unicode-math,

$$
\BbbZ, \mathbb{Z}, \symbb{Z}, ℤ and ^^^^2124 all work.
$$

<!-- flushleft does not work -->
##  Misc math
\begin{flushleft} 
$$\Sigma$$
\end{flushleft} 


Inline:  $\chi$
$$ \Sigma $$
$$ \chi^2 $$
$$ \infty $$
$$ \exists $$
$$ \forall $$
$$ \varTheta $$
$$ \varOmega $$
$$ \varLambda $$
$$ \lambda $$
$\lambda$
$$ \binom{n}{k} $$
$$ a^{-1} $$

\begin{equation}
N_0(\lambda;\varOmega)
\end{equation}

\begin{equation*}
Y = X_{i}^2
\end{equation*}


$$X \sim \mathcal{N}(0, 1)$$

$$X \sim N(0,1)$$

\begin{equation}
y = x^2
\end{equation}
```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      error = TRUE,
                      collapse = T   ) # easier to read
```



emphasis means italics
$$\text{hello \emph{world}} $$
hello $\emph{world}$


###  Summations

### Without Indices

$\sum x_{i}$

$\sum x_{i}^2$

$\sum x_{i}y_{i}$

#### With Indices - Inline Form

$\sum_{i=1}^n x_{i}$

$\sum_{i=1}^n x_{i}^2$

$\sum_{i=1}^n x_{i}y_{i}$

#### With Indices - Display Form

$$\sum_{i=1}^n x_{i}y_{i}$$



### Sets

## requires package (with amsmath? included in yaml at top?) 
  *  knit to pdf has no problem !
  *  knit to html has no problem !  astouding!

$$ \mathbb{Z} $$
$$ \mathbb{pZ} $$
$$ \frac{\mathbb{Z}}{\mathbb{pZ}} $$
$$ Set \{0, 1, 2 , 3 , 4 \}  \in elments of above $$
$$ \left({f}^{}\circ {f}^{-1}\right)\left(x\right) $$
$$ 4^{-1} $$


## Not working:

Verbatim, illustrating spaces
\begin{verbatim*}
Spaces in this text should be indicated.
\end{verbatim*}

Here is regular text.
\begin{quote}
\it{This is indented because it is quoted.}
\end{quote}
Back to regular.

%
% $$ 
% Regular text.
% \begin{quotation} 
% Here I am using verb quotation.
% \begin{flushright}
% {\it - the Author}
% \end{flushright}
% \end{quotation}
% Return to regular text.
% $$



\begin{flushleft}
This is flush left.
\end{flushleft}

## Raw latex
  *  REF:  rmarkdown-cookbook, pandoc will leave as latex
```{=latex}
\begin{tabular}{ll}
A & B \\
A & B \\
\end{tabular}

```{r render, eval=FALSE, include=FALSE 	} 
# for debugging
options(tinytex.verbose = TRUE)

{
  file  <- "0004_math_equations_using_depends.Rmd" 
  file  <- here("MATH", file)
  file  
}
# NOTE:   .tex only works with PDF
# NOTE:    tex will NOT work with html
# in general, pdf will look nicer

output_dir= Sys.getenv("OUTPUT_DIR")
output_dir
rmarkdown::render(file,
                  output_format = "pdf_document",
                  #output_format = "html_document",
                  output_dir = output_dir)
```
