
---
title: "`r knitr::current_input()`"
date: "`r paste('last updated', 
    format(lubridate::now(), ' %d %B %Y'))`"
output:   
  html_document:  
        code_folding: show
        toc: true 
        toc_depth: 2
        toc_float: true
  pdf_document:   
    latex_engine: xelatex  
    toc: true
    toc_depth:  2   
    extra_dependencies: ["amssymb", "bbm", "threeparttable"]
fontsize: 11pt   
geometry: margin=0.5in,top=0.25in   
TAGS: latex, latex: extra_dependencies, 
---


### Embed `modified` latex equations inside Rmd; compile with knitr
### Seems to work Great (as long as no latex packages needed)
? How does next line work?    It is not in $$ ... $$



##  Misc math

$$ \Sigma $$
$$ \chi $$
$$ \chi^2 $$
$$ \infty $$
$$ \exists $$
$$ \forall $$


\begin{equation*}
Y = X_{i}^2
\end{equation*}


$$X \sim \mathcal{N}(0, 1)$$

$$X \sim N(0,1)$$

\begin{equation}
y = x^2
\end{equation}
```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      error = TRUE,
                      collapse = FALSE   ) # easier to read
library(here)
```


```{r library, include=FALSE		}
file  <- knitr::current_input() 
``` 



***

```{r knit_exit(), include = FALSE  , eval=FALSE } 
# knitr::knit_exit()
```


hello $\emph{world}$.


###  Summations

### Without Indices

$\sum x_{i}$

$\sum x_{i}^2$

$\sum x_{i}y_{i}$

#### With Indices - Inline Form

$\sum_{i=1}^n x_{i}$

$\sum_{i=1}^n x_{i}^2$

$\sum_{i=1}^n x_{i}y_{i}$

#### With Indices - Display Form

$$\sum_{i=1}^n x_{i}y_{i}$$

```{r render, eval=FALSE, include=FALSE 	} 
# TODO:  file is found when knitr runs (see above)

# file must be of form:
# dir/name_of_this_file    where dir is relative to project root

file  <- "0005_chi_squared.Rmd"

# NOTE:   .tex only works with PDF
# NOTE:    tex will NOT work with html
# in general, pdf will look nicer


rmarkdown::render(file,
                  output_format = "pdf_document",
                  #output_format = "html_document",
                  output_file = "~/Downloads/print_and_delete/out")
# html works!
```
