
---
title: "`r knitr::current_input()`"
date: "`r paste('last updated', 
    format(lubridate::now(), ' %d %B %Y'))`"
header-includes:
  - \usepackage{amssymb}
  - \usepackage{bbm}
  - \usepackage{threeparttable}
  - \usepackage{forest}
output:   
  html_document:  
        code_folding: show
        toc: true 
        toc_depth: 4
        toc_float: true
        mathjax: default
#       extra_dependencies: ["amssymb", "bbm", "threeparttable", "forest"]
  pdf_document:   
    latex_engine: xelatex  
    toc: true
    toc_depth:  4 
    extra_dependencies: ["amssymb", "bbm", "threeparttable", "forest"]
fontsize: 11pt   
geometry: margin=0.5in,top=0.25in   
TAGS:  math, latex, trees, forest
---

<!--  
as of August 2021
KLUGE to embed the trees (.pdf) in .html file

Step #1   create .pdf file from 0100_latex_trees.Rmd
Step #2   run this file as .html (Take care with location of .pdf) 
-->

#### Embed `modified` latex equations inside Rmd; compile with knitr
Seems to work Great (pdf:  even installs needed latex packages )

#### Latex:  draw trees
\begin{forest}
  for tree={
    fit=band,% spaces the tree out a little to avoid collisions
  }
  [things
    [cabbages, tier=vegetables
      [peaches, tier=fruits]
    ]
    [kings, tier=aristocrats]
    [sealing wax
      [queens, tier=aristocrats
        [carrots, tier=vegetables]
        [pineapple, tier=fruits]
        [aubergine, tier=vegetables]
      ]
    ]
  ]
\end{forest}


```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      error = TRUE,
                      collapse = T   ) # easier to read
```


```{r  pdf_goes_here, out.height = "460px", out.width='800px', echo=F}
## check working dir !   (note:  do not use absolute paths, per Yihui)
knitr::include_graphics("0100_latex_trees.pdf")
```

#### Raw latex
  *  REF:  rmarkdown-cookbook, pandoc will leave as latex
```{=latex}
\begin{tabular}{ll}
A & B \\
A & B \\
\end{tabular}
```

```{r render, eval=FALSE, include=FALSE 	} 
# for debugging
options(tinytex.verbose = TRUE)

getwd()
{
  file <- "MATH/0100_HTML_latex_trees.Rmd"
  file   <-  paste0("~/code/publish_project/", file)
  file
}
# NOTE:   .tex only works with PDF
# NOTE:    tex will NOT work with html
# in general, pdf will look nicer

output_dir= Sys.getenv("OUTPUT_DIR")
output_dir
rmarkdown::render(file,
                  #output_format = "pdf_document",
                  output_format = "html_document",
                  output_dir = output_dir
)
```
