\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}
\usepackage{xcolor}
\usepackage{ulem}


%	PURPOSE:	simple, standalone .tex
% USAGE:		pandoc % -o out.pdf

\begin{document}
 %! TEX root = ~/code/code_publish/MATH/*.tex 
Turn on lsp/latex by using `ft=tex` on bottom vim line (be sure preamble in
place)


\section{Definitions}
Casual Inference - Example patient trials.   Comparing observed outcome. Because
pt can **not be both** w/ treatment and w/o treatment.

Parameter:   Need to estimate.   Maybe mostly **observable** (coef in linear
model, params in model)

Exchangeable:  In joint probability,  $P(x_1,x_2) = P(x_2,x_1)$

\section{Probability}

Power Set: \ $$X \in \mathcal{P}(A)$$

|number of elments | = $2^k$

\section{union/intersection}

$$A \cup B$$ 
$$ \cup_{i=1}^{n}A_{i} $$
$$ \bigcup_{i=1}^{n}A_{i} $$

$$A \cap B$$
$$ \bigcap_{i=1}^{n}A_{i} $$

 
$$ N_h = N * P(H) $$

$$	P(A \mid B)$$



Let $\pi \in [0,1]$ be a random variable.
Then function $f(\pi)$ is probability density function (pdf) if

$$f(\pi) >0    \hspace{10pt} \forall \pi$$

(write P (a-b))
$$\int_\pi f = 1 $$



\section{Measure Space}

\section{Compare Measure Space and Topological Space}

\section{Probability Space}

The Axiom $P(\cup A_i) = \sum P(A_i)$ for countable unions can be viewed as
can sum each indivual element of sample space.

In particular, one 

One model for pdf   of f is **Beta**
which often used in **conjugacy** (same family of distributions for both prior
and posterior,  with only parameters varying)

\section{Bayes}

Let A, B be set of events, such that \

$$A \cap B \neq \emptyset$$

Joint probability: \
$$P(A \cap B) = P(A \hspace{10pt} and \hspace{10pt} B)$$
Conditional probability (show!) 
$$P(B \lvert A) = \frac{P(A \cap B)}{P(A)}$$
Bayes Thm (show!) \ 

$$P(B \mid A) = \frac{P(A \lvert B)P(B)}{P(A)}$$


If D respresents data, and $\theta$ an unknown parameter in our model (ie
hypothesis):
$$p(\theta | D) = \frac{p(D|\theta) p(\theta)} {p(D)}$$


---
\section{Axiom of Choice}
:	Given a family of sets, how to pick ONE representative example from each
set?	

:	Example:	Suppose pool many bags of m\&ms and create a family of sets in
which all the browns are in one set; all the blues in another and so.  Because
all the elements of brown set are the same, how do we pick ONE, ie what is the
rule?

:	For finite sets, can create a rule (proof?).  For infinite, trouble begins.
Hence the need for this axiom.  

\section{topological space}
Let \( \mathcal{T} \) be a topological space, a basis is defined as
\[
 \mathcal{B} = \{B_{\alpha} \in \mathcal{T}\, |\,  U = \bigcup B_{\alpha} \forall U \in \mathcal{T} \}
\]

\end{document}
