---
title:	"0200_tinytex_examples.Rmd"
date:	24DEC2020
mainfont:  "Day Roman" 
output: 
  pdf_document:
    latex_engine: xelatex
    number_sections:  true 
fontsize: 12pt
geometry: margin=0.5in,top=0.25in
---

## Example of .Rmd file (rendered by rmarkdown/knitr as usual)
That ALSO:  
    - Uses TinyTex (R package and Latex distribution)
    - Creates and saves a .tex file (latex)    
    - Renders this .tex file using tinytex::pdflatex()    
And  
    - Renders simple equation with inline Latex cmds.    

##  Pandoc/knitr fail?
  *  try tinytex::parse_install("0200_tinytex_examples.log")

##  TinyTex examples  
  -  TinyTex:: is an R package  
  -  TinyTex is also a lightweight Latex distribtion  
  -  Docs: https://yihui.name/tinytex/  

```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      error = TRUE,
                      collapse = TRUE)

## turn off to limit output
    options(tinytex.verbose = T)

    ## need?  in yaml
    options(tinytex.engine = 'xelatex')

## failure?   try to gleem from .log file
    if (F) {
        tinytex::parse_install("0200_tinytex_examples.log")
}

library(tinytex)
library(rmarkdown)
library(knitr)
```


## Check Tools, tinytex::tlmgr  , pandoc
```{r misc_tools, eval=FALSE  }
# silent, but takes a while
tinytex::tlmgr_update()

# find pandoc
rmarkdown::find_pandoc(cache = FALSE)
# $version
# [1] ‘2.13’
# 
# 
```


## BIG Advantage of useing R package tinytex:: 
  -  if Latex package is missing, it will be installed.

## tinytex::latxmk is wrapper for more common tools?   
  -  pdflatex, etc

```{r example}
getwd()
the_file = "0200_tinytex_examples.Rmd"

if (FALSE ) tinytex::latexmk(the_file)  # file needs *.tex extension

```

##  render latex inline (ie as regular md)

\begin{equation}
x^2 + y^2 = r^2
\end{equation}

## In R, write a .tex file; render it as pdf using tinytex:: 
```{r using_tex_file}

writeLines(c(
             '\\documentclass{article}',
             '\\begin{document}', 'Hello world!', '\\end{document}'
             ), 'test.tex')

tinytex::pdflatex('test.tex', pdf_file="~/Downloads/print_and_delete/out.pdf")
```

markdown_examples/0200_tinytex_examples.Rmd
```{r eval=FALSE  }

file  <- basename("markdown_examples/0200_tinytex_examples.Rmd")
file
rmarkdown::render(file, 
                  output_format="pdf_document",
                  output_dir = "~/Downloads/print_and_delete/")

```



