---
title: "`r knitr::current_input()`"
date: "`r paste('last updated', 
    format(lubridate::now(), ' %d %B %Y'))`"
output:   
  html_document:  
        code_folding: show
        toc: true 
        toc_depth: 4
        toc_float: true
        mathjax: default
  pdf_document:   
    latex_engine: lualatex  
    toc: false
    toc_depth:  4   
fontsize: 11pt   
geometry: margin=0.4in,top=0.25in   
TAGS:    verbatim, pdf:numberLines, bullets, indents, 
---
~/code/MASTER_INDEX.md

PURPOSE:    

(pdf only) \
Code chunk is used to set up code.  Not print or evaluate. \
Instead, use inline r code to print. Use quote to gather unevaluated code;
then eval to get result.   \
Position output as I like or embellish with latex.

USAGE:  rmarkdown::render as usual

```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      error = TRUE,
                      tidy = "styler",
                      strip.white = TRUE,
                      collapse = T   ) # T easier to read
```

```{r library, include=F 		}
# library(jimTools)
``` 
<!-- this is new way to write chunk options -->

```{r cars-plot, include=F,  eval=F}
#| echo = FALSE,
#| message = FALSE,
#| fig.width = 6, 
#| fig.height = 6,
#| fig.path = "figures/",
#| fig.caption = "This is a long caption that fits better inside of a code chunk",
#| fig.alt = "This is a long description that conveys the meaning of the visual."

library(ggplot2)
ggplot2::ggplot(data = mtcars, aes(x = wt, y = mpg)) +
  geom_point()

```

```
This is verbatim.   No mention of r.
```

```{r, attr.source='.numberLines', echo=F}
code  <- quote( if (T) { x <- 1:10; x + 1 })
```

<!-- the ending slash is equivalent to 2 spaces, to latex means end of line -->
`r code` \

Is `code` an R expression?
`r is.expression(code)`

Is `code` a call?
`r is.call(code)` \ 

`r typeof(code)` \


\textcolor{red}{ `r eval(code)`}








```{r render, eval=FALSE, include=FALSE 	} 
output_dir  <- Sys.getenv("OUTPUT_DIR")
output_dir

{
file <- "00303_inline.Rmd"
file  <- normalizePath(file)
file
}

rmarkdown::render(file,
#                  output_format="html_document",
                  output_format="pdf_document",
                  output_dir=output_dir
                  )

```
