---
title: "`r knitr::current_input()`"
date: "`r paste('last updated', 
    format(lubridate::now(), ' %d %B %Y'))`"
output:   
  html_document:  
        code_folding: show
        toc: true 
        toc_depth: 4
        toc_float: true
        mathjax: default
  pdf_document:   
    latex_engine: xelatex  
    toc: true
    toc_depth:  4   
fontsize: 11pt   
geometry: margin=0.4in,top=0.25in   
TAGS:    verbatim, pdf:numberLines, bullets, indents, 
---

#### Bullets and indents.  (html + pdf) 
-   Bullet 1  
    Remember to indent.   And rememb1er to leave 2 spaces after prior line.  
    This is a second part of builet 1.   How will it format?   Will it respect
    Bullet 1 or will it think something else?  
    This is a naother  part of builet 1.   How will it format?   Will it respect
    Bullet 1 or will it think something else?  

    This is still part of bullet 1.  
-   Finally, Bullet 2.  

~/code/MASTER_INDEX.md

```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      error = TRUE,
                      collapse = T   ) # T easier to read
```

```{r library, include=F 		}
# library(jimTools)
``` 

#### verbatim (html + pdf)
```
This is verbatim.   No mention of r.

```

#### print line numbers (pdf only!)
```{r, attr.source='.numberLines'}
if (TRUE) {
  x <- 1:10
  x + 1
}
```




```{r render, eval=FALSE, include=FALSE 	} 
output_dir  <- Sys.getenv("OUTPUT_DIR")
output_dir

{
file <- "./KNITR/0320_knitr_verbatim.Rmd"
file  <- basename(file)

# the_dir  <- dirname(file)
# file  <- file.path(the_dir, file)

file  <- here("KNITR", file)
file
}

rmarkdown::render(file,
                  output_format="html_document",
#                  output_format="pdf_document",
                  output_dir=output_dir
                  )

```
