
---
title: "`r knitr::current_input()`"
date: "`r paste('last updated', 
    format(lubridate::now(), ' %d %B %Y'))`"
output:   
  html_document:  
        code_folding: show
        toc: true 
        toc_depth: 4
        toc_float: true
        mathjax: default
  pdf_document:   
    latex_engine: lualatex  
    toc: true
    toc_depth:  4   
    keep_tex:  true
    keep_md:   true
  header-includes:  
    -  \usepackage{helvet}  
    -  \renewcommand{\familydefault}{\sfdefault}  
    -  \usepackage{ulem}
fontsize: 10pt   
geometry: margin=0.4in,top=0.25in   
TAGS:  skeleton
editor_options: 
  chunk_output_type: console
---
~/code/MASTER_INDEX.md

```{r setup, include=FALSE		}
library(knitr)
library(ggplot2)

## create custom hook `get_label`
knitr::knit_hooks$set(get_label = local({
  function(before, options) {
    if (before) {
      paste("LABEL: ", options$label)
    }
  }
})
)

## global knitr options, including run above hook
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      tidy = "styler",
                      error = TRUE,
                      get_label = TRUE,   # set to run get_label hook to run every chunk 
                      collapse = T   ) # T easier to read

```


<!-- new way to set CHUNK OPTIONS -->

```{r cars-plot, include=F,  eval=F}
#| echo = FALSE,
#| message = FALSE,
#| fig.width = 6, 
#| fig.height = 6,
#| fig.path = "figures/",
#| fig.caption = "This is a long caption that fits better inside of a code chunk",
#| fig.alt = "This is a long description that conveys the meaning of the visual."
```


## create hook_function, called `greet`; `greet` ALSO becomes chunk option 
used to trigger call.
```{r hook_function}
#| greet = TRUE
# To use hook `greet` in a given chunk, specify greet=TRUE
knitr::knit_hooks$set(greet = function(before) {
  if (before) {
    "Hello!" 
    }
})
```

## Example of using hook `greet`
```{r greet=T}
#| greet: TRUE
print("Example of using hook greet")
```


***

REF:  https://github.com/yihui/knitr-examples/blob/master/045-chunk-hook.Rmd

## Three arguments in chunk hooks

A chunk hook has three arguments: `before`, `options` and `envir`. We show how they work through some simple examples.

## 1. The `before` argument


It is a logical argument: `before == TRUE` executes code before a chunk.
Note, first knitr_hooks$set() to set a hook, named `foo1`

```{r set_hooks}
# foo1 will be a function
knitr::knit_hooks$set(foo1 = function(before, options, envir) {
  if (before) {
    '_I appear before a chunk!_\n\n'
  } else {
    '\n\n_I am after a chunk..._'
  }
})

```


## Misc info about knitr hooks
```{r examine}
#| before = TRUE
## knit_hooks is list of functions
knitr::knit_hooks$get("foo1")
if (F) knit_hooks

typeof(knit_hooks)
str(knit_hooks)
typeof(knit_hooks$get)
```

## Example of using hook `foo1`

<!-- trigger foo1 -->
```{r foo1='whatever'}
1+1
```


```{r}
#| foo1 = TRUE
2+2
```

***

## 2. The `options` argument

It contains all the chunk options (include global options) for the current chunk.

```{r render, eval=FALSE, include=FALSE 	} 
output_dir  <- Sys.getenv("OUTPUT_DIR")
output_dir

{
# get file
file <- "0330_knitr_hooks.Rmd"
file  <- normalizePath(file)
file


## Ref only
    # the_dir  <- dirname(file)
    # file  <- basename(file)
    # file  <- file.path(the_dir, file)

}

rmarkdown::render(file,
#                  output_format="html_document",
                    output_format="pdf_document",
                    intermediates_dir='./tmp',
                    clean = F,              # leave tmp files
                    output_dir=output_dir
                  )
```

<!-- #### html ONLY (fonts) -->
```{r, results = 'asis',echo = F}
htmltools::h3("Test big font")
htmltools::h4('Test medium font')
htmltools::h5('Test smaller font')
```
`r htmltools::h3("Outside chunck")`
